My catchy title for a manuscript

### 2017-12-12 code.Rmd
text changes

## General approach

The data com from a series of different experiments. There is one single `xlsx` file with each experiment in a single sheet. A single `csv` file was created from exporting each of those sheets. We will conduct the analysis separated for each experiment. Follows the commented code used for these analyses separated per experiment.

@@

The data were prepared in the wide format where each score for percent perithecia coverage (0 -3) is in a separate colum. Let's transform this dataframe from the wide to the long format using `gather` function of `dplyr`. We need to create a column for the variable name and another for the score.

@@

Let's have a look at the frequency of the scores for each species-genotype separated for each substrate. This is a good plot to show in the paper.

@@

Since we have one species which has two genotypes, it may be important, besides testing the effect of species or genotype in the model, to create a species*genotype interaction variable and fit a mixed model to test the effect of this variable on the perithecial production index (ppi), so that the two genotypes of one species can be compared.

>>>>

## Introduction

The data com from a series of different experiments. There is one single `xlsx` file with each experiment in a single sheet. Follows the commented code used for these analyses separated per experiment.

@@

The data were prepared in the wide format where each score for percent perithecia coverage (0 -3) is in a separate column. Let's transform this dataframe from the wide to the long format using `gather` function of `dplyr`. We need to create a column for the variable name and another for the score.

@@

Let's visualize the frequency of the scores for each species-genotype separated for each substrate. This is a nice plot to show in the paper!

@@

Since we have one species which has two genotypes, it may be important, besides testing the effect of species or genotype in the model, to create a species*genotype interaction variable and fit a mixed model to test the effect of this variable on the perithecial production index (ppi). This way the two genotypes within one species can be compared between them and with the others.

### 2017-12-12 data.Rmd
text changes

The data were obtained from five different, mostly repeated experiments, and were organized in a single `xlsx` file. Data from each experiment are in a separate sheet, which are loaded separately using the `read_excel` function of the `readxl` file.

`I found much more convenient to use this binary file instead of storing in a text file like csv. For some variabeles, I had to deal with some characters which were not loading correctly when using `csv` files.`

Most of the data are already organized in the long format, but some are in the wide, and so will need some transformation. These are done within the respective section of the data analysis page.

>>>>

The data were obtained from five different (mostly repeated in time) experiments, and were organized in a single `xlsx` file. Data from each experiment are in a separate sheet, which are loaded separately by specifying the respective sheet name using the `read_excel` function of the `readxl` file.

**NOTE:** Although text files are prefered to store the data, I found more convenient to use a binary file instead of storing in a text file like csv. For some variabeles, I had to deal with some characters which were not loading correctly when using `csv` files. To visualize the data, go to the respective section of the data analysis page.

Most of the data are already organized in a rectangular (tidy) format, mostly in the long-format (a raw is an observation), but some are in the wide (observations in multiple colums), and so will need some wrangling. This munging is done within the respective section of the data analysis page, after data import.

### 2017-12-12 index.Rmd
text changes

<img src = "https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/PublishingImages/Fusariumdiscyclesm.jpg" align= right width = 250> This is a fully reproducible report that contains and describe the data and the R codes for analyzing and visualizing these data obtained from a series of experiments conducted as an MSc research in the Del Ponte lab. The research's objectives were to assess and compare members of a species complex (FGSC), with varying toxigenic potential, that cause [Fusarium head blight or scab](https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/Pages/Fusarium.aspx), an important disease of wheat and barley worldwide. Several fitness-related traits were compared in five experiments conducted both *in vitro* and in *planta*. Data from each experiment were analyzed separately.

@@

A collection of 30 strains was obtained from the laboratory's FGSC collection and experiments were designed to measure traits related with asexual and sexual fungal growth, pathogenicity towards two wheat cultivars of varying susceptibility and sensitivity to tebuconazole fungicide. In most analyses, we were interested in differences among the species-genotype and not on individual isolates. Therefore, the isolates were treated as random sample representative of the population of strains. In the models, they were treated as random effects (mixed-modeling).

@@

> Del Ponte EM. Title of compendium. Online at https://doi.org/xxx/xxx

@@

## Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.html). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.html). By participating in this project you agree to abide by its terms.

>>>>

<img src = "https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/PublishingImages/Fusariumdiscyclesm.jpg" align= right width = 250> This is a research compendium that contains and describe the data and the R codes for analyzing and visualizing these data obtained from a series of experiments conducted as an MSc research in the Del Ponte lab. The main research's objective was to assess and compare members of a species complex (FGSC), with varying toxigenic potential, that cause [Fusarium head blight or scab](https://www.apsnet.org/edcenter/intropp/lessons/fungi/ascomycetes/Pages/Fusarium.aspx), an important disease of wheat and barley worldwide. Several fitness-related traits were compared in five experiments conducted both *in vitro* and in *planta*. Check the manuscript page.

@@

A collection of 30 strains was obtained from the laboratory's FGSC collection and experiments were designed to measure traits related with asexual and sexual fungal growth, pathogenicity towards two wheat cultivars of varying susceptibility and sensitivity to tebuconazole fungicide. In most analyses, we were interested in testing the effect of species or toxing genotypes, and not the effect of individual isolates. Therefore, the isolates were treated as random sample representative of the population of strains. We used a mixed modeling approach where isolates were treated as random effects.
Data from each experiment were analyzed separately.

@@

> Del Ponte EM. Fitness-related traits of Fusarium graminearum species complex: a research compendia. Online at https://phytopathology.github.io/paper-FGSC-fitness/

@@
